---
title: "AAD Modules Analysis"
author: "Ramie Fathy"
date: "6/25/2020"
output:
  html_document: default
  pdf_document: default
---

#Reading in the functions I'll be using...

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# for data wrangling
library(tidyr)
library(forcats)
library(knitr)
library(stringr)
library(magrittr)
library(dplyr)
library(readxl)
library(ggplot2)
library(tableone)
```

```{r p_table}
p_table <- function(tab_data, ...) {
  tab_data_2 <- deparse(substitute(tab_data))
  
  table_p <- do.call(CreateTableOne, 
                     list(data = as.name(tab_data_2), includeNA = TRUE, ...))
  table_p_out <- print(table_p,
                       showAllLevels = TRUE,
                       printToggle = FALSE)
  kable(table_p_out,
        align = "c")
}
```


#Read in data from spreadsheet

```{r}
aad <- read_xls("AAD Modules Combined.xls", sheet = 1)

nrow(aad) #1174 images reviewed
```

##We reviewed a total of 1174 images, but some duplicates or not clinical images -- let's exclude those

```{r}
# how many clinical images were of patients w/ indeterminate skin type?
nrow(aad %>% filter(fitzpatrick == 4)) # answer: 33

# how many  images were excluded
nrow(aad %>% filter(include == "No" | 
                      fitzpatrick == "Excluded" |
                      dx == "Excluded-NoDx")) # answer: 410

# how many clinical images were duplicates?
nrow(aad %>% filter(duplicate == "Yes")) # answer: 102


aad <- aad %>% 
  filter(fitzpatrick != "Excluded") %>%
  droplevels() %>%
  mutate(module = as.factor(module))  %>% 
  mutate(include = as.factor(include)) %>% 
  mutate(duplicate = as.factor(duplicate)) %>% 
  mutate(fitzpatrick = as.factor(fitzpatrick)) %>% 
  mutate(dx = as.factor(dx)) %>% 
  mutate(coder = as.factor(coder))

data <- aad %>% 
  filter(include == "Yes" & 
           duplicate == "No" & 
           fitzpatrick != "4" &
           dx != "Excluded-NoDx") %>%
  droplevels()
```

##After excluding images that were duplicates (102), non-clinical (410), indeterminate skin type (33), or didn't have an associated diagnosis (3), we're left with 663 images

# Data Exploration

## Let's start with our primary question: what is the distribution of skin types in the AAD Modules' images?

```{r overall score distribution}
p_table(data,
        vars = "fitzpatrick")

ggplot(data = data) +
  geom_histogram(stat = "count", mapping = aes(x = fitzpatrick, fill = "Red")) +
  labs(x = "Skin Type Group", 
       y = "Number of Images with Skin Type", 
       title = "Number of Images with Fitzpatrick Skin Types I/II, III/IV, V/VI") +
  theme_minimal()
```

## Out of curiosity, how do our individual skin type score distributions compare?

```{r individual score distributions}
# table form
p_table(data, 
        vars = "fitzpatrick",
        strata = "coder")

# histogram form
ggplot(data = data) +
  geom_histogram(stat = "count", 
                 mapping = aes(x = coder, fill = fitzpatrick), 
                 position = "fill") +
  labs(x = "Skin Type Group", 
       y = "Number of Images with Skin Type", 
       title = "Number of Images with Fitzpatrick Skin Types I/II, III/IV, V/VI") +
  theme_minimal()

# histogram form, side-by-side
ggplot(data = data) +
  geom_histogram(stat = "count", mapping = aes(x = fitzpatrick, fill = coder)) +
  facet_wrap(~ coder, ncol = 1) +
  labs(x = "Skin Type Group", 
       y = "Number of Images with Skin Type", 
       title = "Number of Images with Fitzpatrick Skin Types I/II, III/IV, V/VI") +
  theme_minimal()
```
##Pretty similar, though RF's lectures seemed to have more 3's than 2's and GO's had fewer 1's than BC/RF 

#By Module

```{r}
# table form
p_table(data, 
        vars = "fitzpatrick",
        strata = "module")


data_byModule <- data %>%
  group_by(module) %>%
    summarise(fitz1 = sum(fitzpatrick == "1"), fitz2 = sum(fitzpatrick == "2"), 
              fitz3 = sum(fitzpatrick == "3"), freq = fitz1/(fitz1+fitz2+fitz3))

order <- data_byModule[order(data_byModule$freq, decreasing = TRUE),]$module

data2 <- data %>% 
  mutate(module = fct_relevel(module, levels = as.character(order)))

# histogram form
ggplot(data = data2) +
  geom_histogram(stat = "count", 
                 mapping = aes(x = module, fill = fitzpatrick), 
                 position = "fill") +
  labs(x = "Skin Type Group", 
       y = "Number of Images with Skin Type", 
       title = "Proportion of Images with Fitzpatrick Skin Types I/II, III/IV, V/VI") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90))


# histogram form
ggplot(data = data2) +
  geom_histogram(stat = "count", 
                 mapping = aes(x = module, fill = fitzpatrick)) +
  labs(x = "Skin Type Group", 
       y = "Number of Images with Skin Type", 
       title = "Number of Images with Fitzpatrick Skin Types I/II, III/IV, V/VI") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90))
```

### still working on figuring out how best to order the above histograms... lmk if you have any ideas

#By Diagnosis

```{r}
# table form...
p_table(data, 
        vars = "dx",
        strata = "fitzpatrick")

### NOTE: combine duplicates with slightly different names, like acne/acne vulgaris
### QUESTION: should we combine the melanomas?
```

## lots of diagnoses... so let's just look at ones with at least five pictures
```{r}
names(which(table(data$dx) > 5))

# gives us 29 diagnoses, a lot easier to work with...
dxs <- names(which(table(data$dx) > 5))

#370 images with those diagnoses
dxs <- data %>% filter(dx %in% dxs) %>% droplevels()

# table form...
p_table(dxs, 
        vars = "dx",
        strata = "fitzpatrick")
```
##The inverse might be more interesting: for each dx, what proportion of images contains patients with each skin type group?
```{r}
# table form...
p_table(dxs, 
        vars = "fitzpatrick",
        strata = "dx")
```


##the following have >10% of images being of patients with FP V/VI skin type:
###acne,
###psorasis,
###pityriasis rosacea,
###rosacea,
###SJS/TEN,
###ulcer

##that's SIX diagnoses... out of the top 29... 
###i.e., 20.7% of the top diagnoses have somewhat decent representation...

##FP III/IV have a few more than that... but not by much: 
###acne,
###atopic dermatitis
###molluscum contagiosum,
###nevus,
###pityriasis rosacea,
###psoriasis,
###purpura,
###rhus dermatitis
###rosacea,
###scabies,
###SJS/TEN,
###squamous cell carcinoma,
###tinea corporis,
###tinea versicolor,
###ulcer


##15/29 of the top 29 diagnoses have over 10% of their images including someone of skin type III/IV
###51.72% -- better, but still not where it should be
###Question is: what is the proportion of the population with these skin types?
###In other words: what should our cutoff for reasonable representation be?

```{r}
#ignore this for now...


# data_byModule <- data %>%
#     count(fitzpatrick, module) %>%
#     mutate(freq = n / sum(n))
# 
# fitz1 <- data_byModule %>% filter(fitzpatrick == "1")
# order <- fitz1[order(data_byModule$freq, decreasing = TRUE),]$module
# 
# data <- merge(x = data, y = data_byModule, by = c("module", "fitzpatrick"))
# 
# freq <- unique(data_byModule %>% filter(fitzpatrick == "1"))$freq
# 
# data2$module <- factor(data2$module, levels = levels(data2$module)[order(-freq)])
```

